Re-run, Repeat, Reproduce, Re-use, Replicate:\\Transforming Code into Scientific Contributions

### 2017-07-17 draft.tex
Update Introduction

Replicability is a cornerstone of science.  If an experimental result cannot be
re-obtained by an independent party, it merely becomes, at best, an observation
that may feed future research (\cite{Mesirov:2010,osc:2015}). Replication
issues have received increased attention in recent years, in the domain of
medicine and psychology in particular (\cite{Iqbal:2016}). One could think that
computer science would mostly be shielded from such issues. But precisely
because it is easy to believe that if a program runs once and gives expected
results it will do so forever, crucial steps to transform working code into
meaningful scientific contributions are rarely undertaken
\citep{Sandve:2013,Schwab:2000}. Computer science is plagued by replication
problems, in part, precisely because it seems impervious to them. In fact, a
program can fail as a scientific contribution in many different ways for many
different reasons. Borrowing the terms coined by \citeauthor{Goble:2016}
\citep{Goble:2016}, for your program to contribute to Science, you have to make
sure it is re-runnable (R$^1$), repeatable (R$^2$), reproducible (R$^3$),
re-usable (R$^4$) and replicable (R$^5$).\\

Let us illustrate this with a very simple example, a random walk written in Python:\\

>>>>

Replicability is a cornerstone of science.  If an experimental result cannot be
re-obtained by an independent party, it merely becomes, at best, an observation
that may inspire future research (\cite{Mesirov:2010,osc:2015}). Replication
issues have received increased attention in recent years, with a particular focus on medicine and psychology (\cite{Iqbal:2016}).
One could think that
computer science would mostly be shielded from such issues, since a computer program
intrinsically describes precisely what it does and is easy to disseminate to other researchers.

But precisely because it is easy to believe that if a program runs once and gives the expected
results it will do so forever, crucial steps to transform working code into
meaningful scientific contributions are rarely undertaken
\citep{Sandve:2013,Schwab:2000}. Computer science is plagued by replication
problems, in part, precisely because it seems impervious to them. In fact, a
program can fail as a scientific contribution in many different ways for many
different reasons. Borrowing the terms coined by \citeauthor{Goble:2016}
\citep{Goble:2016}, for your program to contribute to Science, you have to make
sure it is re-runnable (R$^1$), repeatable (R$^2$), reproducible (R$^3$),
re-usable (R$^4$) and replicable (R$^5$).\\

Let us illustrate this with a small example, a random walk written in Python:\\
